% $Id: pyclips.tex 342 2008-02-22 01:17:23Z Franz $
\documentclass{book}

\input{setup/packages}
\input{setup/macros}

\geometry{%
	letterpaper,
	inner=25mm,
	outer=25mm,
	top=25mm,
	bottom=25mm,
}

\title{
	\pyclips{} Manual\\
	{\small Release 1.0}
}

\author{%
	Francesco Garosi\\
	{\small E-mail: \texttt{franz -dot- g -at- tin -dot- it}}

}

% Please at least include a long-lived email address;
% the rest is at your discretion.
% \authoraddress{
%     E-mail: \email{franz -dot- g -at- tin -dot- it}
% }

% do not mess with the 2 lines below, they are written by make dist
\date{Feb 22, 2008}

\makeindex

\begin{document}

\maketitle

% This makes the contents accessible from the front page of the HTML.
% \ifhtml
% \chapter*{Front Matter\label{front}}
% \fi

\input{copyright}

\begin{abstract}

\noindent
This manual documents the high-level interface to the CLIPS system
provided by the \pyclips{} module. This module allows the creation of a
fully-functional CLIPS environment in a Python session, thus providing
access to a well-known expert systems shell programmatically.

\pyclips{} incorporates most of the API bindings documented in the
\clipsapg{} (freely downloadable from the CLIPS web site, see below) and
embeds these bindings in an Object Oriented layer, incorporating most
CLIPS constructs into Python classes. Instances of these classes allow
access to the status and functionality of the corresponding CLIPS objects.

\end{abstract}

\note{This manual is not intended to be a documentation of CLIPS itself.
CLIPS is extensively documented in several manuals, which are available on
the CLIPS website (see below). A comprehensive tutorial for CLIPS can also
be downloaded. A reasonable knowledge of the CLIPS system is necessary
to understand and use this module.}

\begin{seealso}
	\seetitle[http://www.python.org/]
	{Python Language Web Site}{for information on the Python language}
	\seetitle[http://www.ghg.net/clips/CLIPS.html]
	{CLIPS system web site}{for information on the CLIPS system}
\end{seealso}

\tableofcontents

\input{parts/intro}		% Introduction
\input{parts/contents}	% Module Contents
\input{parts/objects}		% Provided Objects
\input{parts/appendix}        % Appendix and Notes

% \input{parts/license}	        % License Information

\end{document}
